StarCraft Bots and Competitions

### 2015-12-16 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
sscait section reformatted

\subsubsection{SSCAIT 2011.}
Taking place in winter of 2011, the first SSCAIT tournament was organized by Michal \v{C}ertick\'{y} as part of the {\em ``Introduction to Artificial Intelligence''} course at the Department of Applied Informatics, Comenius University in Bratislava, Slovakia. It was inspired by the media coverage of AIIDE StarCraft AI competition held in 2010, but over the following years it diverged from AIIDE competition's format significantly.

@@

@@

The results of SSCAIT seasons 2012-2015 follow:
\begin{itemize}
  \item {\bf 2012:} 52 participants. Student division winners: 
  	\begin{enumerate}
  	  \item Matej Isten\'{i}k's bot
  	  \item Marcin Bartnicki's bot
  	  \item UAlbertaBot
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: ICEBot, after defeating Marcin Bartnicki's bot. 
  \item {\bf 2013:} 50 participants. Student division winner after 1190 round-robin games: 
    \begin{enumerate}
  	  \item Ximp
  	  \item W.O.P.R.
  	  \item UAlbertaBot
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: Krasi0, after defeating ICEBot.
  \item {\bf 2014:} 42 participants. Student division winner after 861 round-robin games: 
    \begin{enumerate}
  	  \item LetaBot
  	  \item W.O.P.R.
  	  \item UAlbertaBot, with the same win rate as W.O.P.R., but with a loss in a mutual game.
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: LetaBot, after defeating Ximp.
  \item {\bf 2015:} At the time of writing this, the SSCAIT 2015 is still in a sandbox phase. 45 bots have registered for the competitive phase so far, including two bots playing as ``Random'' race. The season will be concluded by an elimination bracket featuring 16 bots in 2015.
\end{itemize}

@@

>>>>

\subsubsection{SSCAIT 2011.}
%Taking place in winter of 2011, 
The first SSCAIT tournament was organized by Michal \v{C}ertick\'{y} as part of the {\em ``Introduction to Artificial Intelligence''} course at the Department of Applied Informatics, Comenius University in Bratislava, Slovakia. It was inspired by the media coverage of AIIDE StarCraft AI competition held in 2010, but over the following years it diverged from AIIDE competition's format significantly.

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2012 competition (52 participants)}
\label{tab:sscait2012}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & Matej Isten\'{i}k's bot & 1 & ICEBot \\
2 & Marcin Bartnicki's bot  & 2 & Marcin Bartnicki's bot \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2013 competition (50 participants).
The student division winner was determined by means of 1190 round-robin games}
\label{tab:sscait2013}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & Ximp & 1 & Krasi0 \\
2 & W.O.P.R.  & 2 & ICEBot \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}

%The results of SSCAIT seasons 2012-2015 follow:
%\begin{itemize}
%  \item {\bf 2012:} 52 participants. Student division winners: 
%  	\begin{enumerate}
%  	  \item Matej Isten\'{i}k's bot
%  	  \item Marcin Bartnicki's bot
%  	  \item UAlbertaBot
%  	\end{enumerate}
%  Mixed division winner of the elimination bracket of 8 bots: ICEBot, after defeating Marcin Bartnicki's bot. 
%  \item {\bf 2013:} 50 participants. Student division winner after 1190 round-robin games: 
%    \begin{enumerate}
%  	  \item Ximp
%  	  \item W.O.P.R.
%  	  \item UAlbertaBot
%  	\end{enumerate}
%  Mixed division winner of the elimination bracket of 8 bots: Krasi0, after defeating ICEBot.
%  \item {\bf 2014:} 42 participants. Student division winner after 861 round-robin games: 
%    \begin{enumerate}
%  	  \item LetaBot
%  	  \item W.O.P.R.
%  	  \item UAlbertaBot, with the same win rate as W.O.P.R., but with a loss in a mutual game.
%  	\end{enumerate}
%  Mixed division winner of the elimination bracket of 8 bots: LetaBot, after defeating Ximp.
  %\item {\bf 2015:}

The results of SSCAIT seasons 2012-2014 are provided in the tables~\ref{tab:sscait2012}
to \ref{tab:sscait2014}.  
  At the time of writing this, the SSCAIT 2015 is still in a sandbox phase. 45 bots have registered for the competitive phase so far, including two bots playing as ``Random'' race. The season will be concluded by an elimination bracket featuring 16 bots in 2015.
%\end{itemize}

@@

\begin{table}[!t]
\caption{Ranking of the best bots of the SSCAIT 2014 competition (42 participants).
The student division winner was determined by means of 861 round-robin games}
\label{tab:sscait2014}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Student division} & \multicolumn{2}{|c|}{Mixed division}\\
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Rank} & {\bfseries Bot} \\
\hline
1 & LetaBot & 1 & LetaBot \\
2 & W.O.P.R.  & 2 & Ximp \\
3 & UAlbertaBot 			&   &  \\
\hline
\end{tabular}
\end{table}
